---
title: "Homework01_gapminder"
author: "Conrad Tsang"
date: "18/09/2018"
output: github_document
---

Part of Homework 1 has asked us to create an R Markdown for exploration.  I decided to use Gapminder mainly because the plots at the end were quite mesmerizing to look at.  That and there's *some* relevance to my work in public health.

First we can look at some of the summary statistics of Gapminder.

```{r}
library(gapminder)
summary(gapminder)
```

Then, we can plot Life Expectancy against the year, GDP/capita, and the log of GDP/capita for some visualization.

```{r}
plot(lifeExp ~ year, gapminder)
plot(lifeExp ~ gdpPercap, gapminder)
plot(lifeExp ~ log(gdpPercap), gapminder)
```

Lastly, I just thought it was cool how ggplot could be used to create some gorgeous graphics, although I actually do not truly understand the economic significance behind it -- just very pretty :)

```{r}
library(tidyverse)
p <- ggplot(filter(gapminder, continent != "Oceania"),
            aes(x = gdpPercap, y = lifeExp))
p <- p + scale_x_log10()
p + geom_point(aes(color = continent))
```
