---
title: "Homework01_gapminder"
author: "Conrad Tsang"
date: "18/09/2018"
output: github_document
---

Part of Homework 1 has asked us to create an R Markdown for exploration.  I decided to use Gapminder mainly because the plots at the end were quite mesmerizing to look at.  That and there's *some* relevance to my work in public health, so I'm using this as an opportunity to explore the basics of looking at data if I was thinking about someday analyzing this..

First we can look at some of the summary statistics of Gapminder.

```{r}
library(gapminder)
summary(gapminder)
```

In particular, I'd need to know how many rows and columns there are without needing to add or count the above.

```{r}
nrow(gapminder)
ncol(gapminder)
```

Let's just make sure the data contains the most important country: Canada!

```{r}
attach(gapminder)
any(country == "Canada")
```

Phew!  How many countries are there in gapminder anyway?

```{r}
length(levels(country))
```

Lastly, just wanted to get a sense if there was data missing.

```{r}
any(is.na(gapminder))
```

That took more trial-and-error trying to look up some of the later things above.  I'm glad we'll eventually start to learn how to do this!